---
title: "Epidural Analysis"
author: "Whitney Knauer"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
#| include: false
#| warning: false
#| echo: false

library(epiDisplay)
library(knitr)
library(pROC)
library(tidyverse)
library(readxl)
library(ggplot2)
library(gmodels)
library(ggbeeswarm)
library(dplyr)
library(ggpubr)
library(psych)
library(lme4)
library(Matrix)
library(lmerTest)
library(irr)
library(lmerTest)
library(emmeans)
library(doBy)       
library(gmodels)    
library(car)           
library(cowplot)       
library(gridGraphics)  
library(multcomp)
library(hms)
library(gt)
library(fuzzyjoin)
library(lubridate)
library(data.table)
```

```{r}
#|warning: false
#|echo: false
#|include: false


s1 <- read_csv('data/Bovine Epidural survey 1_July 9, 2025_15.04.csv')
s1 <- s1 |> 
  mutate(
    exp = case_when(
      grepl("^Not at all", Q8) ~ "None",
      grepl("Observed", Q8) & !grepl("Performed", Q8) ~ "Observed",
      grepl("Performed", Q8) ~ "Performed",
      TRUE ~ NA_character_
    )
  )

s1<- s1 |> 
  mutate(
    exp10 = case_when(
      exp == "None"  ~ "none",
      exp == "Observed" ~ "some",
      exp == "Performed" ~ "some"))

s2 <- read_csv('data/Bovine Epidural survey 2_July 9, 2025_15.09.csv')
s2 <- s2 |> 
  mutate(
    exp = case_when(
      grepl("^Not at all", Q8) ~ "None",
      grepl("Observed", Q8) & !grepl("Performed", Q8) ~ "Observed",
      grepl("Performed", Q8) ~ "Performed",
      TRUE ~ NA_character_
    )
  )
s2$year <- as.factor(s2$year)
s2<- s2 |> 
  mutate(
    exp10 = case_when(
      exp == "None"  ~ "none",
      exp == "Observed" ~ "some",
      exp == "Performed" ~ "some"))



prewide <- read_csv('data/prepostwide.csv')
prewide <- prewide |> 
  mutate(
    exp = case_when(
      grepl("^Not at all", Q8pre) ~ "None",
      grepl("Observed", Q8pre) & !grepl("Performed", Q8pre) ~ "Observed",
      grepl("Performed", Q8pre) ~ "Performed",
      TRUE ~ NA_character_
    )
  )

#Making stuff numeric so we can calculate a delta
prewide<-prewide |> 
  mutate(
    Q10prenum = case_when(
      Q10pre == "Strongly disagree"         ~ 1, 
      Q10pre == "Somewhat disagree"         ~ 2, 
      Q10pre == "Neither agree nor disagree" ~ 3, 
      Q10pre == "Somewhat agree"            ~ 4, 
      Q10pre == "Strongly agree"            ~ 5
    )
  )

prewide<-prewide |> 
  mutate(
    Q10postnum = case_when(
      Q10post == "Strongly disagree"         ~ 1, 
      Q10post == "Somewhat disagree"         ~ 2, 
      Q10post == "Neither agree nor disagree" ~ 3, 
      Q10post == "Somewhat agree"            ~ 4, 
      Q10post == "Strongly agree"            ~ 5
    )
  )

prewide<-prewide |> 
  mutate(
    Q10delta = Q10postnum - Q10prenum
  )

prewide<-prewide |> 
  mutate(
    Q11prenum = case_when(
      Q11pre == "Strongly disagree"         ~ 1, 
      Q11pre == "Somewhat disagree"         ~ 2, 
      Q11pre == "Neither agree nor disagree" ~ 3, 
      Q11pre == "Somewhat agree"            ~ 4, 
      Q11pre == "Strongly agree"            ~ 5
    )
  )

prewide<-prewide |> 
  mutate(
    Q11postnum = case_when(
      Q11post == "Strongly disagree"         ~ 1, 
      Q11post == "Somewhat disagree"         ~ 2, 
      Q11post == "Neither agree nor disagree" ~ 3, 
      Q11post == "Somewhat agree"            ~ 4, 
      Q11post == "Strongly agree"            ~ 5
    )
  )

prewide<-prewide |> 
  mutate(
    Q11delta = Q11postnum - Q11prenum
  )


prelong <- read_csv('data/prepostlong.csv')
prelong <- prelong |> 
  mutate(
    exp = case_when(
      grepl("^Not at all", Q8) ~ "None",
      grepl("Observed", Q8) & !grepl("Performed", Q8) ~ "Observed",
      grepl("Performed", Q8) ~ "Performed",
      TRUE ~ NA_character_
    )
  )

both <- read_csv('data/prepostlongboth.csv')
both<- both |> 
    mutate(
    exp = case_when(
      grepl("^Not at all", Q8) ~ "None",
      grepl("Observed", Q8) & !grepl("Performed", Q8) ~ "Observed",
      grepl("Performed", Q8) ~ "Performed",
      TRUE ~ NA_character_
    )
  )
both$year <- as.factor(both$year)
both<- both |> 
  mutate(
    exp10 = case_when(
      exp == "None"  ~ "none",
      exp == "Observed" ~ "some",
      exp == "Performed" ~ "some"))
  

```

## Some Description of the Data/Participants

```{r}

table(s1$year)
table(s2$year)

table(prelong$prepost, prelong$year)

table(prewide$year)

table (prelong$Prenopost, prelong$year)
table (prelong$Postnopre, prelong$year)


```

Students who completed the pre-survey (n=37 in 2024; n=33 in 2025)

Students who completed the post-survey (n=24 in 2024; n=31 in 2025)

Students who complete pre but not post survey (n=13 in 2024; n=5 in 2025)

Students who completed the post survey but not the pre (n=0 in 2024; n=3 in 2025)

Students who completed both: 24 in 2024 and 28 in 2025 (n=52 complete surveys). This is the data I used for the delta chance and change in attitude models (only students with complete data).

## Student Experience with Epidurals (s1)

First, for all students who completed the pre-survey

```{r}


#How much experience have you had with bovine epidural prior to this course? Select all that applies:
table(s1$Q8)
table(s1$exp)
table(s1$exp10)

#When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task under supervision.
table(s1$Q10)
unique(s1$Q10)

#Q11 When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task unsupervised.
table(s1$Q11)

#Q12: When learning a new practical task or skill, the chance to perform that task or skill on a model enhances the learning process.
table(s1$Q12)



```

## Student Experience with Epidurals (s2)

First, for all students who completed the post survey

```{r}

#How much experience have you had with bovine epidural prior to this course? Select all that applies:
table(s2$Q8)
table(s2$exp)
table(s2$exp10)

#When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task under supervision.
table(s2$Q10)


#Q11 When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task unsupervised.
table(s2$Q11)

```

## Delta Change in Attitude and Change Model

```{r}
#When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task under supervision.
table (prewide$Q10prenum)
table(prewide$Q10postnum)
table(prewide$Q10delta)


#When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task unsupervised.
table (prewide$Q11prenum)
table(prewide$Q11postnum)
table(prewide$Q11delta)

#using the long format, with only students who completed both the pre and post survey (n=52 students)
#Q10 When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task under supervision.
table(both$Q10)
table(both$Q10, both$year)
table(both$Q10, both$exp)
table(both$Q10, both$exp10)

#yes significant: After training on the model, students were much more likely to feel confident performing a bovine epidural under supervision.
both$Q10 <- factor(both$Q10, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q10~ prepost +  exp10, data = both, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Q11 When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task unsupervised.
table(both$Q11)
table(both$Q11, both$year)
table(both$Q11, both$prepost)

#yes significant: After training on the model, students were much more likely to feel confident performing a bovine epidural unsupervised.
both$Q11 <- factor(both$Q11, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q11~ prepost + exp10, data = both, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))



```

## Post Survey

```{r}

#10a The epidural model is a useful tool for the acquisition of skills required to complete an epidural injection on a bovine.
table(s2$Q10a)
table(s2$Q10a, s2$year)
table(s2$Q10a, s2$exp)
table(s2$Q10a, s2$exp10)


#year, no difference. Experience (either observing or performing) sig (less likely to be in a higher category)
s2$Q10a <- factor(s2$Q10a, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q10a~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#11a The use of the model has reinforced my previous learning.
table(s2$Q11a)
table(s2$Q11a, s2$year)
table(s2$Q11a, s2$exp)

#year no difference, experience no difference
s2$Q11a <- factor(s2$Q11a, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q11a~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#12 The use of the model has duplicated my previous learning.
table(s2$Q12)
table(s2$Q12, s2$exp10)
table(s2$Q12, s2$year)

#not year, not experience sig
s2$Q12 <- factor(s2$Q12, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q12~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#13 My range of manual dexterity skills have increased as a result of using this epidural model.
table(s2$Q13)
table(s2$Q13, s2$year)
table(s2$Q13, s2$exp)

#not year, not experience
s2$Q13 <- factor(s2$Q13, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q13~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#14 My manual dexterity skills have improved as a result of using this epidural model.
table(s2$Q14)
table(s2$Q14, s2$year)
table(s2$Q14, s2$exp)

#not year, not experience
s2$Q14 <- factor(s2$Q14, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q14~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Q15 I received feedback from an instructor after I used the epidural model.
table(s2$Q15)
table(s2$Q15, s2$year)
table(s2$Q15, s2$exp)

#not year, not experience
s2$Q15 <- factor(s2$Q15, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q15~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#16 As a result of using the model, I now feel more confident to perform an epidural injection on a bovine.
table(s2$Q16)
table(s2$Q16, s2$year)
table(s2$Q16, s2$exp)

#not year, not experience
s2$Q16 <- factor(s2$Q16, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q16~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#17 The skills I have learnt using the model will be valuable to me during my clinical year.
table(s2$Q17)
table(s2$Q17, s2$year)
table(s2$Q17, s2$exp)

#not year, not experience
s2$Q17 <- factor(s2$Q17, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q17~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))






```
