---
title: "Epidural Analysis"
author: "Whitney Knauer"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
    toc_float: true
---

```{r}
#| include: false
#| warning: false
#| echo: false

library(epiDisplay)
library(knitr)
library(pROC)
library(tidyverse)
library(readxl)
library(ggplot2)
library(gmodels)
library(ggbeeswarm)
library(dplyr)
library(ggpubr)
library(psych)
library(lme4)
library(Matrix)
library(lmerTest)
library(irr)
library(lmerTest)
library(emmeans)
library(doBy)       
library(gmodels)    
library(car)           
library(cowplot)       
library(gridGraphics)  
library(multcomp)
library(hms)
library(gt)
library(fuzzyjoin)
library(lubridate)
library(data.table)
library(extrafont)
```

```{r}
#|warning: false
#|echo: false
#|include: false


s1 <- read_csv('data/Bovine Epidural survey 1_July 9, 2025_15.04.csv')
s1 <- s1 |> 
  mutate(
    exp = case_when(
      grepl("^Not at all", Q8) ~ "None",
      grepl("Observed", Q8) & !grepl("Performed", Q8) ~ "Observed",
      grepl("Performed", Q8) ~ "Performed",
      TRUE ~ NA_character_
    )
  )

s1<- s1 |> 
  mutate(
    exp10 = case_when(
      exp == "None"  ~ "none",
      exp == "Observed" ~ "some",
      exp == "Performed" ~ "some"))

s2 <- read_csv('data/Bovine Epidural survey 2_July 9, 2025_15.09.csv')
s2 <- s2 |> 
  mutate(
    exp = case_when(
      grepl("^Not at all", Q8) ~ "None",
      grepl("Observed", Q8) & !grepl("Performed", Q8) ~ "Observed",
      grepl("Performed", Q8) ~ "Performed",
      TRUE ~ NA_character_
    )
  )
s2$year <- as.factor(s2$year)
s2<- s2 |> 
  mutate(
    exp10 = case_when(
      exp == "None"  ~ "none",
      exp == "Observed" ~ "some",
      exp == "Performed" ~ "some"))



prewide <- read_csv('data/prepostwide.csv')
prewide <- prewide |> 
  mutate(
    exp = case_when(
      grepl("^Not at all", Q8pre) ~ "None",
      grepl("Observed", Q8pre) & !grepl("Performed", Q8pre) ~ "Observed",
      grepl("Performed", Q8pre) ~ "Performed",
      TRUE ~ NA_character_
    )
  )

#Making stuff numeric so we can calculate a delta
prewide<-prewide |> 
  mutate(
    Q10prenum = case_when(
      Q10pre == "Strongly disagree"         ~ 1, 
      Q10pre == "Somewhat disagree"         ~ 2, 
      Q10pre == "Neither agree nor disagree" ~ 3, 
      Q10pre == "Somewhat agree"            ~ 4, 
      Q10pre == "Strongly agree"            ~ 5
    )
  )

prewide<-prewide |> 
  mutate(
    Q10postnum = case_when(
      Q10post == "Strongly disagree"         ~ 1, 
      Q10post == "Somewhat disagree"         ~ 2, 
      Q10post == "Neither agree nor disagree" ~ 3, 
      Q10post == "Somewhat agree"            ~ 4, 
      Q10post == "Strongly agree"            ~ 5
    )
  )

prewide<-prewide |> 
  mutate(
    Q10delta = Q10postnum - Q10prenum
  )

prewide<-prewide |> 
  mutate(
    Q11prenum = case_when(
      Q11pre == "Strongly disagree"         ~ 1, 
      Q11pre == "Somewhat disagree"         ~ 2, 
      Q11pre == "Neither agree nor disagree" ~ 3, 
      Q11pre == "Somewhat agree"            ~ 4, 
      Q11pre == "Strongly agree"            ~ 5
    )
  )

prewide<-prewide |> 
  mutate(
    Q11postnum = case_when(
      Q11post == "Strongly disagree"         ~ 1, 
      Q11post == "Somewhat disagree"         ~ 2, 
      Q11post == "Neither agree nor disagree" ~ 3, 
      Q11post == "Somewhat agree"            ~ 4, 
      Q11post == "Strongly agree"            ~ 5
    )
  )

prewide<-prewide |> 
  mutate(
    Q11delta = Q11postnum - Q11prenum
  )


prelong <- read_csv('data/prepostlong.csv')
prelong <- prelong |> 
  mutate(
    exp = case_when(
      grepl("^Not at all", Q8) ~ "None",
      grepl("Observed", Q8) & !grepl("Performed", Q8) ~ "Observed",
      grepl("Performed", Q8) ~ "Performed",
      TRUE ~ NA_character_
    )
  )

both <- read_csv('data/prepostlongboth.csv')
both<- both |> 
    mutate(
    exp = case_when(
      grepl("^Not at all", Q8) ~ "None",
      grepl("Observed", Q8) & !grepl("Performed", Q8) ~ "Observed",
      grepl("Performed", Q8) ~ "Performed",
      TRUE ~ NA_character_
    )
  )
both$year <- as.factor(both$year)
both<- both |> 
  mutate(
    exp10 = case_when(
      exp == "None"  ~ "none",
      exp == "Observed" ~ "some",
      exp == "Performed" ~ "some"))
  

osce <- read_csv('data/OSCE results.csv')


```

## Some Description of the Data/Participants

```{r}

table(s1$year)
table(s2$year)

table(prelong$prepost, prelong$year)

table(prewide$year)

table (prelong$Prenopost, prelong$year)
table (prelong$Postnopre, prelong$year)


```

Students who completed the pre-survey (n=37 in 2024; n=33 in 2025)

Students who completed the post-survey (n=24 in 2024; n=31 in 2025)

Students who complete pre but not post survey (n=13 in 2024; n=5 in 2025)

Students who completed the post survey but not the pre (n=0 in 2024; n=3 in 2025)

Students who completed both: 24 in 2024 and 28 in 2025 (n=52 complete surveys). This is the data I used for the delta chance and change in attitude models (only students with complete data).

## Student Experience with Epidurals (s1)

### First, for all students who completed the pre-survey

```{r}


#How much experience have you had with bovine epidural prior to this course? Select all that applies:
table(s1$Q8)
table(s1$exp)
table(s1$exp10)

#When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task under supervision.
table(s1$Q10)
unique(s1$Q10)

#Q11 When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task unsupervised.
table(s1$Q11)

#Q12: When learning a new practical task or skill, the chance to perform that task or skill on a model enhances the learning process.
table(s1$Q12)



```

### Stacked Bar Charts for S1 only (Q10,11,12)

```{r}

df <- data.frame(
  Group = c("Q10", "Q11", "Q12"),
  Strongly_Disagree = c(9, 59, 0),
  Disagree = c(27, 16, 0),
  Neutral = c(9, 4, 0),
  Agree = c(27, 14, 21),
  Strongly_Agree = c(28, 7, 79)
)

df_long <- df |> 
  pivot_longer(cols = -Group, names_to = "Rating", values_to = "Percentage")

df_long$Group <- factor(df_long$Group, levels = rev(df$Group))  
df_long$Rating <- factor(df_long$Rating, 
                         levels = rev(c("Strongly_Disagree", "Disagree", "Neutral", "Agree", "Strongly_Agree")))

ggplot(df_long, aes(x = Percentage, y = Group, fill = Rating)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
      geom_text(
            aes(label = ifelse(Percentage > 0, Percentage, "")),
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4, 
            family = "Times New Roman") + 
  scale_fill_brewer(palette = "Blues", direction = -1,
                    labels = c("Strongly Agree", "Agree", "Neutral", "Disagree", "Strongly Disagree"), 
                     guide = guide_legend(nrow = 1, reverse = TRUE)) +  
  labs(x = "Percentage of Respondents (%)", y = "", fill = "") +
  theme_classic()+
  theme (legend.position = "top", 
         legend.direction = "horizontal", 
              axis.text = element_text(color = "black", size=10), 
               legend.text = element_text(color = "black", size=10))+
                theme(text=element_text(size=12, family = "Times New Roman"))







```

### Models exploring year and experience with the epidural procedure

```{r}

#look at experience...some vs. none

#When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task under supervision.
table(s1$Q10)

s1$Q10 <- factor(s1$Q10, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q10~ year + exp, data = s1, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Q11 When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task unsupervised.
table(s1$Q11)

s1$Q11 <- factor(s1$Q11, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q11~ year + exp10, data = s1, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))



```

## Student Experience with Epidurals (s2)

### First, for all students who completed the post survey

```{r}

#How much experience have you had with bovine epidural prior to this course? Select all that applies:
table(s2$Q8)
table(s2$exp)
table(s2$exp10)

#When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task under supervision.
table(s2$Q10)


#Q11 When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task unsupervised.
table(s2$Q11)

```

### Stacked Bar Charts

```{r}
df <- data.frame(
  Group = c("Q10", "Q11"),
  Strongly_Disagree = c(0, 0),
  Disagree = c(0, 5),
  Neutral = c(0, 7),
  Agree = c(13, 62),
  Strongly_Agree = c(87, 25)
)

df_long <- df |> 
  pivot_longer(cols = -Group, names_to = "Rating", values_to = "Percentage")

df_long$Group <- factor(df_long$Group, levels = rev(df$Group))  
df_long$Rating <- factor(df_long$Rating, 
                         levels = rev(c("Strongly_Disagree", "Disagree", "Neutral", "Agree", "Strongly_Agree")))

ggplot(df_long, aes(x = Percentage, y = Group, fill = Rating)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
      geom_text(
             aes(label = ifelse(Percentage > 0, Percentage, "")),
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4, 
            family = "Times New Roman") + 
  scale_fill_brewer(palette = "Blues", direction = -1,
                    labels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"), 
                     guide = guide_legend(nrow = 1)) +  
  labs(x = "Percentage of Respondents (%)", y = "", fill = "") +
  theme_classic()+
  theme (legend.position = "none", 
         legend.direction = "horizontal", 
              axis.text = element_text(color = "black", size=10), 
               legend.text = element_text(color = "black", size=10))+
                theme(text=element_text(size=12, family = "Times New Roman"))
 




```

## Delta Change in Attitude and Change Model

### Summarized Data

```{r}
#When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task under supervision.
table (prewide$Q10prenum)
table(prewide$Q10postnum)
table(prewide$Q10delta)

prewide |> 
  summarize(
    meandelta = mean(Q10delta), 
    sd = sd(Q10delta)
  )


#When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task unsupervised.
table (prewide$Q11prenum)
table(prewide$Q11postnum)
table(prewide$Q11delta)

prewide |> 
  summarize(
    meandelta = mean(Q11delta), 
    sd = sd(Q11delta)
  )



```

### Stacked Bar Charts

```{r}

df <- data.frame(
  Group = c("Q10 pre", "Q10 post", "Q11 pre", "Q11 post"),
  Strongly_Disagree = c(4, 0, 52, 0),
  Disagree = c(29, 0, 17, 4),
  Neutral = c(12, 0, 6, 8),
  Agree = c(23, 10, 17, 62),
  Strongly_Agree = c(33, 90, 8, 27)
)

df_long <- df |> 
  pivot_longer(cols = -Group, names_to = "Rating", values_to = "Percentage")

df_long$Group <- factor(df_long$Group, levels = rev(df$Group))  
df_long$Rating <- factor(df_long$Rating, 
                         levels = rev(c("Strongly_Disagree", "Disagree", "Neutral", "Agree", "Strongly_Agree")))

ggplot(df_long, aes(x = Percentage, y = Group, fill = Rating)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
      geom_text(
            aes(label = ifelse(Percentage > 0, Percentage, "")),
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4, 
            family = "Times New Roman") + 
  scale_fill_brewer(palette = "Blues", direction = -1,
                    labels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"), 
                     guide = guide_legend(nrow = 1)) +  
  labs(x = "Percentage of Respondents (%)", y = "", fill = "") +
  theme_classic()+
  theme (legend.position = "none", 
         legend.direction = "horizontal", 
              axis.text = element_text(color = "black", size=10), 
               legend.text = element_text(color = "black", size=10))+
                theme(text=element_text(size=12, family = "Times New Roman"))







```

### Diverging Stacked Bar Chart

#### Option 1

```{r}

#add neutral to the side

df <- data.frame(
  Group = c("Q10 pre", "Q10 post", "Q11 pre", "Q11 post"),
  Strongly_Disagree = c(4, 0, 52, 0),
  Disagree = c(29, 0, 17, 4),
  Neutral = c(12, 0, 6, 8),
  Agree = c(23, 10, 17, 62),
  Strongly_Agree = c(33, 90, 8, 27)
)

# Reshape to long format
df_long <- df %>% 
  pivot_longer(cols = -Group, names_to = "Rating", values_to = "Percentage") |> 
  mutate(
    # Set factor levels for ordered stacking
    Rating = factor(Rating, levels = c("Strongly_Disagree", "Disagree", "Neutral", "Strongly_Agree", "Agree")),
    
    # Flip sign for negative responses to diverge
    PercentSigned = case_when(
      Rating %in% c("Strongly_Disagree", "Disagree") ~ -Percentage,
      TRUE ~ Percentage
    )
  )

# Reverse group order for visual stacking top-down
df_long$Group <- factor(df_long$Group, levels = rev(unique(df$Group)))

# Plot
ggplot(df_long, aes(x = PercentSigned, y = Group, fill = Rating)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
  geom_text(aes(label = Percentage),
            position = position_stack(vjust = 0.5),
            size = 3, color = "black") +
  scale_fill_manual(
    values = c(
      "Strongly_Disagree" = "#d73027",
      "Disagree" = "#fc8d59",
      "Neutral" = "#cccccc",
      "Agree" = "#91bfdb",
      "Strongly_Agree" = "#4575b4"
    ),
    labels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"),
    guide = guide_legend(nrow = 1)
  ) +
  labs(x = "Percentage of Respondents (%)", y = "", fill = "") +
  theme_classic() +
  theme(
    legend.position = "top",
    legend.text = element_text(color = "black", size = 10),
    axis.text = element_text(color = "black", size = 10)
  )
```

#### Option 2

```{r}

df <- data.frame(
  Group = c("Q10 pre", "Q10 post", "Q11 pre", "Q11 post"),
  Strongly_Disagree = c(4, 0, 52, 0),
  Disagree = c(29, 0, 17, 4),
  Neutral = c(12, 0, 6, 8),
  Agree = c(23, 10, 17, 62),
  Strongly_Agree = c(33, 90, 8, 27)
)

# Reshape to long format
df_long <- df %>% 
  pivot_longer(cols = -Group, names_to = "Rating", values_to = "Percentage") |> 
  mutate(
    # Set factor levels for ordered stacking
    Rating = factor(Rating, levels = c("Strongly_Disagree", "Disagree", "Neutral", "Strongly_Agree", "Agree")),
    
    # Flip sign for negative responses to diverge
    PercentSigned = case_when(
      Rating %in% c("Strongly_Disagree", "Disagree", "Neutral") ~ -Percentage,
      TRUE ~ Percentage
    )
  )

# Reverse group order for visual stacking top-down
df_long$Group <- factor(df_long$Group, levels = rev(unique(df$Group)))

# Plot
ggplot(df_long, aes(x = PercentSigned, y = Group, fill = Rating)) +
  geom_bar(stat = "identity", position = "stack", color = "black")+
  geom_text(aes(label = ifelse(Percentage > 0, Percentage, "")),
            position = position_stack(vjust = 0.5),
            size = 3, color = "black", 
            family = "Times New Roman")  +
  scale_fill_manual(
    values = c(
      "Strongly_Disagree" = "#d73027",
      "Disagree" = "#fc8d59",
      "Neutral" = "#cccccc",
      "Agree" = "#91bfdb",
      "Strongly_Agree" = "#4575b4"), 
     breaks = c("Strongly_Disagree", "Disagree", "Neutral", "Agree", "Strongly_Agree"),  # << desired legend order
  labels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree")
) +
  theme_classic() +
  labs(x = "Percentage of Respondents (%)", y = "", fill = "") +
  theme_classic() +
  theme(
    legend.position = "top",
    legend.text = element_text(color = "black", size = 10),
    axis.text = element_text(color = "black", size = 10)
  )+
  scale_x_continuous(limits = c(-100, 100), breaks = seq(-100, 100, by = 50))+
                theme(text=element_text(size=12, family = "Times New Roman"))
  
  
  
  
  
  


```

### Models

```{r}

#using the long format, with only students who completed both the pre and post survey (n=52 students)
#Q10 When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task under supervision.
table(both$Q10)
table(both$Q10, both$year)
table(both$Q10, both$exp)
table(both$Q10, both$exp10)

#yes significant: After training on the model, students were much more likely to feel confident performing a bovine epidural under supervision.
both$Q10 <- factor(both$Q10, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
both$prepost <- factor(both$prepost) 
both$prepost <- relevel(both$prepost, ref = "pre")
model <- polr(Q10~ prepost, data = both, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Q11 When next presented with the opportunity to perform a bovine epidural injection on a living animal, I feel confident to complete this task unsupervised.
table(both$Q11)
table(both$Q11, both$year)
table(both$Q11, both$prepost)

#yes significant: After training on the model, students were much more likely to feel confident performing a bovine epidural unsupervised.
both$Q11 <- factor(both$Q11, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
both$prepost <- factor(both$prepost) 
both$prepost <- relevel(both$prepost, ref = "pre")
model <- polr(Q11~ prepost, data = both, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))
```

### 

## Post Survey

### Data and Models

```{r}

#10a The epidural model is a useful tool for the acquisition of skills required to complete an epidural injection on a bovine.
table(s2$Q10a)
table(s2$Q10a, s2$year)
table(s2$Q10a, s2$exp)
table(s2$Q10a, s2$exp10)


#year, no difference. Experience (either observing or performing) sig (less likely to be in a higher category)
s2$Q10a <- factor(s2$Q10a, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q10a~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#11a The use of the model has reinforced my previous learning.
table(s2$Q11a)
table(s2$Q11a, s2$year)
table(s2$Q11a, s2$exp)

#year no difference, experience no difference
s2$Q11a <- factor(s2$Q11a, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q11a~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#12 The use of the model has duplicated my previous learning.
table(s2$Q12)
table(s2$Q12, s2$exp10)
table(s2$Q12, s2$year)

#not year, not experience sig
s2$Q12 <- factor(s2$Q12, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q12~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#13 My range of manual dexterity skills have increased as a result of using this epidural model.
table(s2$Q13)
table(s2$Q13, s2$year)
table(s2$Q13, s2$exp)

#not year, not experience
s2$Q13 <- factor(s2$Q13, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q13~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#14 My manual dexterity skills have improved as a result of using this epidural model.
table(s2$Q14)
table(s2$Q14, s2$year)
table(s2$Q14, s2$exp)

#not year, not experience
s2$Q14 <- factor(s2$Q14, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q14~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Q15 I received feedback from an instructor after I used the epidural model.
table(s2$Q15)
table(s2$Q15, s2$year)
table(s2$Q15, s2$exp)

#not year, not experience
s2$Q15 <- factor(s2$Q15, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q15~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#16 As a result of using the model, I now feel more confident to perform an epidural injection on a bovine.
table(s2$Q16)
table(s2$Q16, s2$year)
table(s2$Q16, s2$exp)

#not year, not experience
s2$Q16 <- factor(s2$Q16, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q16~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#17 The skills I have learnt using the model will be valuable to me during my clinical year.
table(s2$Q17)
table(s2$Q17, s2$year)
table(s2$Q17, s2$exp)

#not year, not experience
s2$Q17 <- factor(s2$Q17, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Strongly agree"), ordered = TRUE)
model <- polr(Q17~ as.factor(year) + exp10, data = s2, Hess=TRUE)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))






```

### Stacked Bar Chart

```{r}
df <- data.frame(
  Group = c("Q10", "Q11", "Q10a", "Q11a", "Q12", "Q13", "Q14", "Q15", "Q16", "Q17"),
  Strongly_Disagree = c(0, 0, 0, 0, 4, 0, 0, 0, 0, 0),
  Disagree = c(0, 5, 5, 2, 13, 4, 4, 9, 2, 2),
  Neutral = c(0, 7, 6, 9, 33, 36, 35, 4, 9, 7),
  Agree = c(13, 62, 36, 42, 30, 38, 36, 42, 34, 29),
  Strongly_Agree = c(87, 26, 53, 47, 20, 22, 25, 45, 55, 62)
)

df_long <- df |> 
  pivot_longer(cols = -Group, names_to = "Rating", values_to = "Percentage")

df_long$Group <- factor(df_long$Group, levels = rev(df$Group))  
df_long$Rating <- factor(df_long$Rating, 
                         levels = rev(c("Strongly_Disagree", "Disagree", "Neutral", "Agree", "Strongly_Agree")))

ggplot(df_long, aes(x = Percentage, y = Group, fill = Rating)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
      geom_text(
             aes(label = ifelse(Percentage > 0, Percentage, "")),
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4, 
            family = "Times New Roman") + 
  scale_fill_brewer(palette = "Blues", direction = -1,
                    labels = c("Strongly Agree", "Agree", "Neutral", "Disagree", "Strongly Disagree"), 
                     guide = guide_legend(nrow = 1, reverse = TRUE)) +  
  labs(x = "Percentage of Respondents (%)", y = "", fill = "") +
  theme_classic()+
  theme (legend.position = "top", 
         legend.direction = "horizontal", 
              axis.text = element_text(color = "black", size=10), 
               legend.text = element_text(color = "black", size=10))+
                theme(text=element_text(size=12, family = "Times New Roman"))






```

## OSCE Summary

### Overall

```{r}
#Student chooses correct needle size and gauge
table(osce$Q1)

#Student manipulates the tail to find the correct location
table(osce$Q2)

#Student maintains a clean hand
table(osce$Q3)

#Student inserts needle in the appropriate joint
table(osce$Q4)

#Student inserts the needle at the proper angle
table(osce$Q5)

#Student inserts the needle with the bevel facing cranially
table(osce$Q6)

#Student demonstrates the bubble or hanging frop technique to check for the appropriate location
table(osce$Q7)

#Student uses two hands to attach the syringe
table(osce$Q8)

#total summarized score
table(osce$Score)

osce |> 
  summarise(
    mscore = mean(Score),
    sdscore = sd(Score), 
    ranges = range(Score)
  )





```

### Difference by year?

```{r}
#Student chooses correct needle size and gauge
Q1tab <- table(osce$Q1, osce$Year)
Q1tab
fisher.test(Q1tab)

#Student manipulates the tail to find the correct location
Q2tab<- table(osce$Q2, osce$Year)
Q2tab
fisher.test(Q2tab)

#Student maintains a clean hand
Q3tab <- table(osce$Q3, osce$Year)
Q3tab
fisher.test(Q3tab)

#Student inserts needle in the appropriate joint
Q4tab<-table(osce$Q4, osce$Year)
Q4tab
fisher.test(Q4tab)

#Student inserts the needle at the proper angle
Q5tab<- table(osce$Q5, osce$Year)
Q5tab
fisher.test(Q5tab)

#Student inserts the needle with the bevel facing cranially
Q6tab <- table(osce$Q6, osce$Year)
Q6tab
fisher.test(Q6tab)

#Student demonstrates the bubble or hanging drop technique to check for the appropriate location
Q7tab <- table(osce$Q7, osce$Year)
Q7tab
fisher.test(Q7tab)

#Student uses two hands to attach the syringe
Q8tab<-table(osce$Q8, osce$Year)
Q8tab
fisher.test(Q8tab)

#total summarized score
table(osce$Score)
osce |> 
  group_by(Year) |> 
  summarize(
    mean = mean(Score), 
    sd = sd(Score)
  )
t.test(Score ~ Year, data=osce)

```

Students in the 2025 cohort more likely to have a "0" in uses a hanging drop and using two hands to attach the syringe, and had overall lower scores.
